Towards Comparable Active Learning

### 2024-06-03 doc/al_benchmark_paper.tex
paper und ergebnisse
Moved the Introduction of the synthetic datasets and related experiments to a seperate section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Datasets}\label{sec:datasets}
A detailed description of the preprocessing of each dataset can be found in Appendix \ref{app:hyperparameters}. \\ [1mm]
\textbf{Tabular:}
AL research conducted on tabular data is sparse (only \cite{ashdeep} from the considered baseline papers). 
We, therefore, introduce a set of tabular datasets that we selected according to the following criteria:
(i) They should be solvable by medium-sized models in under 1000 samples, (ii) the gap between most AL algorithms and random sampling should be significant (potential for AL is present) and (iii) the gap between the AL algorithms and our oracle should also be significant (research on these datasets can produce further lifts).
We use \textbf{Splice}, \textbf{DNA} and \textbf{USPS} from LibSVMTools \cite{libsvmtools}.\\
\textbf{Image:}
We use \textbf{FashionMNIST} \cite{xiao2017fashion} and \textbf{Cifar10} \cite{krizhevsky2009learning}, since both are widely used in AL literature.\\
\textbf{Text:}
We use \textbf{News Category} \cite{misra2022news} and \textbf{TopV2} \cite{chen-etal-2020-low-resource}.
Text datasets have seen less attention in AL research, but most of the papers that evaluate on text (\cite{hu2021towards}, \cite{zhou2021towards}) use at least one of these datasets.\\ [1mm]
We would like to point out that these datasets are selected for speed of computation (both in terms of number of features and necessary budget to solve the dataset). 
However, similar to our argumentation for picking smaller classifiers, we are solely focused on comparing different AL algorithms in this paper and do not aim to develop novel classification models on these datasets.
Our assumption is that a well-performing algorithm in our benchmark will also generalize well to larger real-world datasets, because we included multiple different data domains and classifier sizes in our experiments. \\ [1mm]
Adapting the experimental setting from \cite{hacohen2022active}, we offer all our datasets in the un-encoded (normal) setting as well as pre-encoded by a fixed embedding model that was trained by unsupervised contrastive learning. 
The text datasets are an exception to this, as they are only offered in their encoded form.
The pre-encoded datasets enable us to test single-sample algorithms on more complex datasets like Cifar10 and FashionMnist.
They also serve the purpose of investigating the interplay between self-supervised learning techniques and AL, as well as alleviating the cold-start problem described in \cite{luth2024navigating} as they require a way smaller seed set.
The classification model for every encoded dataset is a single linear layer with softmax activation.
The embedding model was trained with the SimCLR \cite{chen2020simple} algorithm adopting the protocol from \cite{hacohen2022active}. 
%For Cifar10 and FashionMnist we adapt the reported hyperparameters from \cite{hacohen2022active} and for the tabular datasets we use random search to optimize the hyperparameters.
To ensure that enough information from the data is encoded by our embedding model, the quality of embeddings during pretext training was measured after each epoch.
We attached a linear classification head to the encoder, fine-tuned it to the data and evaluated this classifier for test accuracy, mirroring our AL setup for embedded datasets. 
The checkpoint of each encoder model will be provided together with the framework. \\ [1mm]
\textbf{Synthetic Data}
Existing AL algorithms can broadly be categorized into two types, uncertainty \cite{wang2014new, gal2017deep} - and geometric-approaches \cite{sener2017active, hacohen2022active, ashdeep}. 
Both types have principled shortcomings in terms of the utilized information that makes them unsuitable for certain data distributions.
To test for these shortcomings, we created two synthetic datasets, namely "Honeypot" and "Diverging Sine", that are hard to solve for methods focused on the classifier's decision boundary or data clustering respectively. 
To avoid algorithms memorizing these datasets they are generated during the experiment, depending on $s_\D$. \\
	\includegraphics[width=0.4\linewidth]{img/diverging_sin.jpg}
	\includegraphics[width=0.4\linewidth]{img/honeypot.jpg}
	\caption{Synthetic "Honeypot" and "Diverging Sine" datasets. The decision boundary is not part of the dataset and serves only as a visual guide.}
        \label{fig:synthDataAppendix}
Honeypot creates to two easy to distinguish clusters with 150 samples each and one overlapping "honeypot" that represents a noisy region of the dataset with potentially miss-labeled, miss-measured or generally adverse samples.
This honeypot contains 150 samples of each class, creating a balance of 50\% beneficial samples and 50\% adverse samples in the dataset.
The honeypot is located on the likely decision boundary of a classifier that is trained on the beneficial samples to maximize its negative impact on purely uncertainty based acquisition functions.
Diverging Sine samples the datapoints for each class from two diverging sinusoidal functions that are originating from the same y-intercept.
This creates a challenging region one the left hand side, where a lot of datapoints need to be sampled and an easy region on the right hand side, where very few datapoints are enough. 
The repeating nature of a sin function encourages diversity based acquisition functions to equally sample the entire length, drastically oversampling the right hand side of the dataset.
Each class has 500 datapoints. \\ [1mm]
Every dataset has a fixed size for the seed set of 1 sample per class, with the only exceptions being un-encoded FashionMnist and Cifar10 with 100 examples per class to alleviate the cold-start problem in these complex domains.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classification Model}\label{sec:choosing_the_classifier}
\begin{wraptable}{R}{0.65\textwidth}
    \vspace{-0.7cm}
    \caption{Overview of available batch sizes for each dataset}
    \vspace{0.1cm}
    \label{tab:batch_sizes}
    \begin{tabular}{l|c|c|c|c|c|c|c|c}
                    & B & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
         \hline
        Enc. DNA    & 40 & o & o &&&&& \\
        Honeypot    & 60 & o & o &&&&& \\
        Diverging Sine& 60 & o & o &&&&& \\
        Enc. Splice & 100 & o & o & o & o &&&\\
        TopV2       & 200 & o & o & o & o &&& \\
        Splice      & 400 & o & o & o & o & o && \\
        DNA         & 300 & o & o & o & o & o && \\
        USPS        & 400 & o & o & o & o & o && \\
        Enc. Cifar10& 450 & o & o & o & o & o && \\
        Enc. FMnist & 500 & o & o & o & o & o && \\
        Enc. USPS   & 600 & o & o & o & o & o && \\
        News        & 3K &&& o & o & o & o &\\
        FMnist      & 10K &&&&&& o & o\\
        Cifar10     & 10K &&&&&& o & o \\
    \end{tabular}
    \vspace{-0.35cm}
\end{wraptable}
The model $\hat y$ can be trained in two ways. Either the parameters of the model are reset to a fixed initial setting $\hat y^{(0)}$ after each AL iteration and the classifier is trained from scratch with the updated labeled set $\mathcal{L}^{(i)}$, or the previous state $\hat y^{(i-1)}$ is retained and the classifier is fine-tuned on $\mathcal{L}^{(i)}$ for a reduced number of epochs.
In this work, we use the fine-tuning method for un-encoded datasets to save computational time, while we use the from-scratch training for embedded datasets since they have very small classifiers and this approach generally produces better results.
Our fine-tuning scheme always trains for at least one epoch and employs an aggressive early stopping with a patience of 2 afterwards.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}
\begin{table}[]
	\caption{Performances for acquisition functions on real-world datasets, aggregated for un-encoded and encoded datasets. Performance is shown as average ranks over restarts (1.0 is the best rank). Algorithms are sorted by aggregated performance on un-encoded datasets. }
	\label{tab:results}
          & Splice & DNA  & USPS 		 	& Cfr10 & FMnist & TopV2 & News  & Un-enc. & Enc. \\
Oracle  & 1.0 $\pm$ 0.01 & 1.0 $\pm$ 0.01 & 1.0 $\pm$ 0.0   & 1.0 $\pm$ 0.0   & 1.0 $\pm$ 0.0   & 1.0 $\pm$ 0.01 & 1.0 $\pm$ 0.0  & 1.0 & 2.0 \\
Margin  & 6.6 $\pm$ 0.02 & 4.3 $\pm$ 0.01 & 2.1 $\pm$ 0.01  & 6.3 $\pm$ 0.01  & 4.4 $\pm$ 0.0   & 2.4 $\pm$ 0.01 & 3.7 $\pm$ 0.0  & 4.3 & 4.2 \\
Badge   & 5.2 $\pm$ 0.01 & 6.3 $\pm$ 0.01 & 2.9 $\pm$ 0.01  & 5.2 $\pm$ 0.01  & 4.7 $\pm$ 0.0   & 3.3 $\pm$ 0.01 & 3.5 $\pm$ 0.0  & 4.5 & 5.4 \\
LeastConf & 9.2 $\pm$ 0.02 & 10.3 $\pm$ 0.02 & 8.1 $\pm$ 0.02  & 2.1 $\pm$ 0.01 & 4.0 $\pm$ 0.0   & 7.9 $\pm$ 0.02  & 3.0 $\pm$ 0.01  & 6.4  & 6.5 \\
DSA     & 7.4 $\pm$ 0.02 & 7.3 $\pm$ 0.01 & 7.5 $\pm$ 0.01  & 5.4 $\pm$ 0.01  & 5.1 $\pm$ 0.0   & 6.0 $\pm$ 0.02 & 7.3 $\pm$ 0.01 & 6.6 & 6.7 \\
BALD    & 4.0 $\pm$ 0.01 & 4.7 $\pm$ 0.01 & 5.4 $\pm$ 0.01  & 12.0 $\pm$ 0.01 & 7.6 $\pm$ 0.0   & 7.6 $\pm$ 0.02 & 5.0 $\pm$ 0.0  & 6.6 & 7.6 \\
CoreGCN & 6.9 $\pm$ 0.01 & 4.9 $\pm$ 0.01 & 10.4 $\pm$ 0.01 & 7.6 $\pm$ 0.01  & 6.5 $\pm$ 0.01  & 4.0 $\pm$ 0.01 & 6.8 $\pm$ 0.0  & 6.7 & 8.2 \\
Entropy & 6.6 $\pm$ 0.02 & 3.9 $\pm$ 0.01 & 7.6 $\pm$ 0.01  & 7.6 $\pm$ 0.01  & 4.9 $\pm$ 0.01  & 9.8 $\pm$ 0.02 & 9.6 $\pm$ 0.0  & 7.1 & 6.5 \\
LSA     & 6.1 $\pm$ 0.01 & 6.8 $\pm$ 0.01 & 5.3 $\pm$ 0.01  & 7.7 $\pm$ 0.01  & 10.6 $\pm$ 0.01 & 7.5 $\pm$ 0.01 & 7.3 $\pm$ 0.01 & 7.3 & 7.5 \\
Random  & 9.0 $\pm$ 0.01 & 9.3 $\pm$ 0.01 & 5.3 $\pm$ 0.01  & 8.4 $\pm$ 0.01  & 11.1 $\pm$ 0.0  & 7.9 $\pm$ 0.01 & 8.0 $\pm$ 0.0  & 8.4 & 6.9 \\
Coreset        & 7.1 $\pm$ 0.01 & 9.0 $\pm$ 0.01  & 10.5 $\pm$ 0.01 & 6.8 $\pm$ 0.01 & 7.1 $\pm$ 0.0   & 8.5 $\pm$ 0.02  & 10.8 $\pm$ 0.01 & 8.5  & 7.2 \\
TypiClust      & 8.8 $\pm$ 0.01 & 10.2 $\pm$ 0.01 & 12.0 $\pm$ 0.02 & 7.9 $\pm$ 0.01 & 11.0 $\pm$ 0.01 & 12.0 $\pm$ 0.02 & 12.0 $\pm$ 0.01 & 10.5 & 9.2
\begin{figure}
    \caption{Ranks of each acquisition function aggregated by domain. Horizontal bars indicate a \textbf{non}-significant rank difference. The significance is tested via a paired-t-test with $\alpha=0.05$.}
    \label{fig:ranks_by_domain}
    \includegraphics[width=0.49\linewidth]{img/macro_vector.jpg}
    \includegraphics[width=0.49\linewidth]{img/macro_text.jpg}
    \includegraphics[width=0.49\linewidth]{img/macro_img.jpg}
    \includegraphics[width=0.49\linewidth]{img/macro_enc.jpg}
\begin{figure}
    \caption{Results for all acquisition functions on both synthetic datasets.}
    \label{fig:main_body_result}
    \includegraphics[width=0.49\linewidth]{img/micro_honeypot.jpg}
    \includegraphics[width=0.49\linewidth]{img/micro_diverging_sin.jpg}
Storing the results of every run in a separate file allows us to create various aggregates.
Apart from plotting standard performance curves and reporting their AUC values per dataset (Fig. \ref{fig:main_body_result}), we primarily rely on ranks to aggregate the performance of an acquisition function across datasets.
For each dataset, the AUC values of all acquisition functions are sorted and assigned a rank based on position, with the best rank being 1.
These ranks can safely be averages across datasets as they are no longer subjected to scaling differences of each dataset.
In Table \ref{tab:results} we provide the rank of each acquisition function per dataset and averaged for each (un-)encoded dataset. 
Please note, that for Tab \ref{tab:results} we are averaging not only over runs, but also over query sizes per dataset. 
For the results per query size, please refer to App. \ref{app:auc_by_query_size}. \\
Additionally, we provide aggregated ranks per data domain in Fig. \ref{fig:ranks_by_domain}, revealing varying performances of acquisition functions like DSA/LSA, BALD and CoreGCN.
The leading algorithms Margin-Sampling and BADGE show very stable performance across all tested data domains. \\ [1mm]
Results for the Honeypot dataset reveal expected shortcomings of uncertainty sampling algorithms like margin, entropy and least confident sampling as well as BALD.
In addition, BADGE is underperforming for this dataset compared to real-world data. 
Results for Diverging Sine also confirm expected behavior, as clustering algorithms (Coreset, TypiClust) fall behind uncertainty algorithms (Entropy-, Margin-Sampling), with the exception of BADGE. \\
We provide a very small ablation study on the importance of the embeddings by testing a version of Coreset and TypiClust on this dataset that does not use the embeddings produced by the classification model, but rather clusters the data directly.
"Coreset Raw" and "TypiClust Raw" both perform worse than their embedding-based counterpart.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Datasets}\label{sec:datasets}
A detailed description of the preprocessing of each dataset can be found in Appendix \ref{app:hyperparameters}. \\ [1mm]
\textbf{Tabular:}
AL research conducted on tabular data is sparse (only \cite{ashdeep} from the considered baseline papers). 
We, therefore, introduce a set of tabular datasets that we selected according to the following criteria:
(i) They should be solvable by medium-sized models in under 1000 samples, (ii) the gap between most AL algorithms and random sampling should be significant (potential for AL is present) and (iii) the gap between the AL algorithms and our oracle should also be significant (research on these datasets can produce further lifts).
We use \textbf{Splice}, \textbf{DNA} and \textbf{USPS} from LibSVMTools \cite{libsvmtools}.\\
\textbf{Image:}
We use \textbf{FashionMNIST} \cite{xiao2017fashion} and \textbf{Cifar10} \cite{krizhevsky2009learning}, since both are widely used in AL literature.\\
\textbf{Text:}
We use \textbf{News Category} \cite{misra2022news} and \textbf{TopV2} \cite{chen-etal-2020-low-resource}.
Text datasets have seen less attention in AL research, but most of the papers that evaluate on text (\cite{hu2021towards}, \cite{zhou2021towards}) use at least one of these datasets.\\ [1mm]
%
We would like to point out that these datasets are selected for speed of computation (both in terms of number of features and necessary budget to solve the dataset). 
However, similar to our argumentation for picking smaller classifiers, we are solely focused on comparing different AL algorithms in this paper and do not aim to develop novel classification models on these datasets.
Our assumption is that a well-performing algorithm in our benchmark will also generalize well to larger real-world datasets, because we included multiple different data domains and classifier sizes in our experiments. \\ [1mm]
Adapting the experimental setting from \cite{hacohen2022active}, we offer all our datasets in the un-encoded (normal) setting as well as pre-encoded by a fixed embedding model that was trained by unsupervised contrastive learning. 
The text datasets are an exception to this, as they are only offered in their encoded form.
The pre-encoded datasets enable us to test single-sample algorithms on more complex datasets like Cifar10 and FashionMnist.
They also serve the purpose of investigating the interplay between self-supervised learning techniques and AL, as well as alleviating the cold-start problem described in \cite{luth2024navigating} as they require a way smaller seed set.
The classification model for every encoded dataset is a single linear layer with softmax activation.
The embedding model was trained with the SimCLR \cite{chen2020simple} algorithm adopting the protocol from \cite{hacohen2022active}. 
%For Cifar10 and FashionMnist we adapt the reported hyperparameters from \cite{hacohen2022active} and for the tabular datasets we use random search to optimize the hyperparameters.
To ensure that enough information from the data is encoded by our embedding model, the quality of embeddings during pretext training was measured after each epoch.
We attached a linear classification head to the encoder, fine-tuned it to the data and evaluated this classifier for test accuracy, mirroring our AL setup for embedded datasets. 
The checkpoint of each encoder model will be provided together with the framework. \\ [1mm]
Every dataset has a fixed size for the seed set of 1 sample per class, with the only exceptions being un-encoded FashionMnist and Cifar10 with 100 examples per class to alleviate the cold-start problem in these complex domains.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classification Model}\label{sec:choosing_the_classifier}
\begin{wraptable}{R}{0.65\textwidth}
    \vspace{-0.7cm}
    \caption{Overview of available batch sizes for each dataset}
    \vspace{0.1cm}
    \label{tab:batch_sizes}
    \begin{tabular}{l|c|c|c|c|c|c|c|c}
                    & B & 1 & 5 & 20 & 50 & 100 & 500 & 1000 \\
         \hline
        Enc. DNA    & 40 & o & o &&&&& \\
        Enc. Splice & 100 & o & o & o & o &&&\\
        TopV2       & 200 & o & o & o & o &&& \\
        Splice      & 400 & o & o & o & o & o && \\
        DNA         & 300 & o & o & o & o & o && \\
        USPS        & 400 & o & o & o & o & o && \\
        Enc. Cifar10& 450 & o & o & o & o & o && \\
        Enc. FMnist & 500 & o & o & o & o & o && \\
        Enc. USPS   & 600 & o & o & o & o & o && \\
        News        & 3K &&& o & o & o & o &\\
        FMnist      & 10K &&&&&& o & o\\
        Cifar10     & 10K &&&&&& o & o \\
    \end{tabular}
    \vspace{-0.35cm}
\end{wraptable}
The model $\hat y$ can be trained in two ways. Either the parameters of the model are reset to a fixed initial setting $\hat y^{(0)}$ after each AL iteration and the classifier is trained from scratch with the updated labeled set $\mathcal{L}^{(i)}$, or the previous state $\hat y^{(i-1)}$ is retained and the classifier is fine-tuned on $\mathcal{L}^{(i)}$ for a reduced number of epochs.
In this work, we use the fine-tuning method for un-encoded datasets to save computational time, while we use the from-scratch training for embedded datasets since they have very small classifiers and this approach generally produces better results.
Our fine-tuning scheme always trains for at least one epoch and employs an aggressive early stopping with a patience of 2 afterwards.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}
%
\begin{table}[]
	\caption{Performances for acquisition functions on real-world datasets, aggregated for un-encoded and encoded datasets. Performance is shown as average ranks over restarts (1.0 is the best rank). Algorithms are sorted by aggregated performance on un-encoded datasets. }
	\label{tab:results}
	\centering
        \resizebox{\columnwidth}{!}{
\begin{tabular}{l|lllllll|ll}
          & Splice & DNA  & USPS 		 	& Cfr10 & FMnist & TopV2 & News  & Un-enc. & Enc. \\
          \hline
Oracle  & 1.0 $\pm$ 0.01 & 1.0 $\pm$ 0.01 & 1.0 $\pm$ 0.0   & 1.0 $\pm$ 0.0   & 1.0 $\pm$ 0.0   & 1.0 $\pm$ 0.01 & 1.0 $\pm$ 0.0  & 1.0 & 2.0 \\
Margin  & 6.6 $\pm$ 0.02 & 4.3 $\pm$ 0.01 & 2.1 $\pm$ 0.01  & 6.3 $\pm$ 0.01  & 4.4 $\pm$ 0.0   & 2.4 $\pm$ 0.01 & 3.7 $\pm$ 0.0  & 4.3 & 4.2 \\
Badge   & 5.2 $\pm$ 0.01 & 6.3 $\pm$ 0.01 & 2.9 $\pm$ 0.01  & 5.2 $\pm$ 0.01  & 4.7 $\pm$ 0.0   & 3.3 $\pm$ 0.01 & 3.5 $\pm$ 0.0  & 4.5 & 5.4 \\
LeastConf & 9.2 $\pm$ 0.02 & 10.3 $\pm$ 0.02 & 8.1 $\pm$ 0.02  & 2.1 $\pm$ 0.01 & 4.0 $\pm$ 0.0   & 7.9 $\pm$ 0.02  & 3.0 $\pm$ 0.01  & 6.4  & 6.5 \\
DSA     & 7.4 $\pm$ 0.02 & 7.3 $\pm$ 0.01 & 7.5 $\pm$ 0.01  & 5.4 $\pm$ 0.01  & 5.1 $\pm$ 0.0   & 6.0 $\pm$ 0.02 & 7.3 $\pm$ 0.01 & 6.6 & 6.7 \\
BALD    & 4.0 $\pm$ 0.01 & 4.7 $\pm$ 0.01 & 5.4 $\pm$ 0.01  & 12.0 $\pm$ 0.01 & 7.6 $\pm$ 0.0   & 7.6 $\pm$ 0.02 & 5.0 $\pm$ 0.0  & 6.6 & 7.6 \\
CoreGCN & 6.9 $\pm$ 0.01 & 4.9 $\pm$ 0.01 & 10.4 $\pm$ 0.01 & 7.6 $\pm$ 0.01  & 6.5 $\pm$ 0.01  & 4.0 $\pm$ 0.01 & 6.8 $\pm$ 0.0  & 6.7 & 8.2 \\
Entropy & 6.6 $\pm$ 0.02 & 3.9 $\pm$ 0.01 & 7.6 $\pm$ 0.01  & 7.6 $\pm$ 0.01  & 4.9 $\pm$ 0.01  & 9.8 $\pm$ 0.02 & 9.6 $\pm$ 0.0  & 7.1 & 6.5 \\
LSA     & 6.1 $\pm$ 0.01 & 6.8 $\pm$ 0.01 & 5.3 $\pm$ 0.01  & 7.7 $\pm$ 0.01  & 10.6 $\pm$ 0.01 & 7.5 $\pm$ 0.01 & 7.3 $\pm$ 0.01 & 7.3 & 7.5 \\
Random  & 9.0 $\pm$ 0.01 & 9.3 $\pm$ 0.01 & 5.3 $\pm$ 0.01  & 8.4 $\pm$ 0.01  & 11.1 $\pm$ 0.0  & 7.9 $\pm$ 0.01 & 8.0 $\pm$ 0.0  & 8.4 & 6.9 \\
Coreset        & 7.1 $\pm$ 0.01 & 9.0 $\pm$ 0.01  & 10.5 $\pm$ 0.01 & 6.8 $\pm$ 0.01 & 7.1 $\pm$ 0.0   & 8.5 $\pm$ 0.02  & 10.8 $\pm$ 0.01 & 8.5  & 7.2 \\
TypiClust      & 8.8 $\pm$ 0.01 & 10.2 $\pm$ 0.01 & 12.0 $\pm$ 0.02 & 7.9 $\pm$ 0.01 & 11.0 $\pm$ 0.01 & 12.0 $\pm$ 0.02 & 12.0 $\pm$ 0.01 & 10.5 & 9.2
\end{tabular}
       	}
\end{table}
%
\begin{figure}
    \centering
    \caption{Ranks of each acquisition function aggregated by domain. Horizontal bars indicate a \textbf{non}-significant rank difference. The significance is tested via a paired-t-test with $\alpha=0.05$.}
    \label{fig:ranks_by_domain}
    \includegraphics[width=0.49\linewidth]{img/macro_vector.jpg}
    \includegraphics[width=0.49\linewidth]{img/macro_text.jpg}
    \includegraphics[width=0.49\linewidth]{img/macro_img.jpg}
    \includegraphics[width=0.49\linewidth]{img/macro_enc.jpg}
\end{figure}
%

Storing the results of every run in a separate file allows us to create various aggregates.
Apart from plotting standard performance curves and reporting their AUC values per dataset (Fig. \ref{fig:main_body_result}), we primarily rely on ranks to aggregate the performance of an acquisition function across datasets.
For each dataset, the AUC values of all acquisition functions are sorted and assigned a rank based on position, with the best rank being 1.
These ranks can safely be averages across datasets as they are no longer subjected to scaling differences of each dataset.
In Table \ref{tab:results} we provide the rank of each acquisition function per dataset and averaged for each (un-)encoded dataset. 
Please note, that for Tab \ref{tab:results} we are averaging not only over runs, but also over query sizes per dataset. 
For the results per query size, please refer to App. \ref{app:auc_by_query_size}. \\
Additionally, we provide aggregated ranks per data domain in Fig. \ref{fig:ranks_by_domain}, revealing varying performances of acquisition functions like DSA/LSA, BALD and CoreGCN.
The leading algorithms Margin-Sampling and BADGE show very stable performance across all tested data domains. \\ [1mm]

\include{synthetic_datasets}
